\paperTitle

### 2014-05-16 doc/icml2014/background.tex

Next, we assume the graphical model only has conditional independences given by
the graph:
\begin{assumption}[Faithful]
  \label{prop:ci}  
  For any hidden variables $a,b,c \in \bh$
  such that there is an active trail between $a$ and $b$ conditioned on $c$,
  we have that $a$ and $b$ are dependent given $c$ (i.e., $a\not\perp b \given c$).
\end{assumption}

@@

%It is easy to see that $\LearnMarginals$ has a polynomial sample complexity
%because it composes two parts that individually have polynomial sample
%complexity.
%From \citet{anandkumar13tensor} given the non-degeneracy assumptions
  %\assumptionref{non-degeneracy},
  We have that $\mOpphat{v}{i}$
  converges to $\mOpp{v}{i}$ at a rate of $n^{-\frac12}$ with a constant
  that depends polynomially on the $k$-th singular value of
  $\mOpp{v}{i}$.
% PL: we don't have a crisp theorem (because there's multiple paths), so leave it vague.
%Recovering the marginals $Z_\sC$ from the conditional moments via $\LearnClique$ is a linear operation and thus also has polynomial sample complexity. 
However, $\sigma_{k}(\mOpp{v}{i})$ can become extremely
small if $h_i$ and $x_v$ are connected via many intermediate hidden variables.

>>>>

Next, we assume the graphical model only has conditional independences given by
the graph:
\begin{assumption}[Faithful]
  \label{prop:ci}  
  For any hidden variables $a,b,c \in \bh$
  such that there is an active trail\footnote{See
  \citet{koller2009probabilistic} for a definition.} between $a$ and $b$ conditioned on $c$,
  we have that $a$ and $b$ are dependent given $c$ (i.e., $a\not\perp b \given c$).
\end{assumption}

@@

%It is easy to see that $\LearnMarginals$ has a polynomial sample complexity
%because it composes two parts that individually have polynomial sample
%complexity.
%From \citet{anandkumar13tensor} given the non-degeneracy assumptions
  %\assumptionref{non-degeneracy},
  We have that $\mOpphat{v}{i}$
  converges to $\mOpp{v}{i}$ at a rate of $n^{-\frac12}$ with a constant
  that depends polynomially on the $k$-th singular value of
  $\mOpp{v}{i}$.
% PL: we don't have a crisp theorem (because there's multiple paths), so leave it vague.
%Recovering the marginals $Z_\sC$ from the conditional moments via $\LearnClique$ is a linear operation and thus also has polynomial sample complexity. 
However, $\sigma_{k}(\mOpp{v}{i})$ can become extremely
small if $h_i$ and $x_v$ are connected via many intermediate hidden
variables.\footnote{To see this, consider a chain-structured graphical model:
$h_1 \to h_2 \cdots \to h_t \to x_v$. In this example, if
$\sigma_k(\Pr(h_{i+1} \given h_{i})) \ge \sigma_k$ for each $i = 1,
\cdots, t-1$, then $\sigma_k(\mOpp{v}{1})$ can be as bad as
$\sigma_k^t \sigma_k(\mOpp{v}{t})$.}.
